\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-01-02 draft.tex
remove references to strong bindings from into paragraphs to sec:rigid and sec:objfcn

\section{Rigid Tariffs with Endogenous Political Pressure}
\label{sec:rigid}
In this section and the next, I demonstrate the implications of taking account of endogenous political pressure on some central design features of trade agreements. I do this by first summarizing the essential results from \Textcite{bs2005} for the design of trade agreements when political considerations are exogenous and then compare them to the case under consideration here of endogenous political activity aimed at gaining protectionist tariffs.

@@

\section{Political Objective Functions and the Role of Trade Agreements}
\label{sec:objfcn}
The previous sections analyze in general the effects of various forms of trade agreements when political pressure is endogenous. I now use the specific functional forms for the economy given in Section~\ref{sec:stage} and compare government objective functions to understand the impact of strong bindings, weak bindings and escape clauses on government welfare.

>>>>

\section{Rigid Tariffs with Endogenous Political Pressure}
\label{sec:rigid}
In this section and the next, I demonstrate the implications of taking account of endogenous political pressure on some central design features of trade agreements. I begin by developing some basic results about the design of trade agreements with tariff caps when political pressure is endogenous. I then compare these results to those from from \Textcite{bs2005} for the design of trade agreements when political considerations are exogenous.

@@

\section{Political Objective Functions and the Role of Trade Agreements}
\label{sec:objfcn}
The previous sections analyze in general the effects of various forms of trade agreements when political pressure is endogenous. I now use the specific functional forms for the economy given in Section~\ref{sec:stage} and compare government objective functions to understand the impact of trade agreements on government welfare.
